\huge The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-05-04 Writeup/kohler_clarke_2021.tex
naming convention notes.

A wallpaper group is a topologically discrete group of isometries of the Euclidean plane, i.e. transformations that preserve distance \citep{RN1425}. Wallpaper groups differ in the number and kind of these transformations. In mathematical group theory, when the elements of one group is completely contained in another, the inner group is called a subgroup of the outer group \citep{RN1425}. The full list of subgroup relationships is listed in Section 1.4.2 of the Supplementary Material. Subgroup relationships between wallpaper groups can be distinguished by their indices. The index of a subgroup relationship is the number of cosets, i.e. the number of times the subgroup is found in the supergroup \citep{RN1425}. As an example, let us consider groups \textit{P2} and \textit{P6}. If we ignore the translations in two directions that both groups share, group \textit{P6} consists of the set of rotations \{$0^{\circ}$, $60^{\circ}$, $120^{\circ}$, $180^{\circ}$, $240^{\circ}$, $300^{\circ}$\}, in which \textit{P2} \{$0^{\circ}$, $180^{\circ}$\} is contained. \textit{P2} is thus a subgroup of \textit{P6}, and \textit{P6} can be generated by combining \textit{P2} with rotations \{$0^{\circ}$, $120^{\circ}$, $240^{\circ}$\}. Because \textit{P2} is repeated three times in \textit{P6}, \textit{P2} is a subgroup of \textit{P6} with index 3 \citep{RN1425}. The 17 wallpaper groups thus obey a hierarchy of complexity where simpler groups are subgroups of more complex ones \citep{RN1711}.

>>>>

A wallpaper group is a topologically discrete group of isometries of the Euclidean plane, i.e. transformations that preserve distance \citep{RN1425}. Wallpaper groups differ in the number and kind of these transformations \textcolor{OliveGreen}{and we can uniquely refer to different groups using crystallographic notation. Full details of this naming convention can be found XXXX, but in brief, most groups are notated by $PXZ$, where $X\in\{1,2,3,4,6\}$ indicates the highest order of rotational symmetry and $Z\in\{m, g\}$ indicates whether the pattern contains \textit{m}irror or \textit{g}lide symmetry. For example, $P4$ contains 4 fold rotation, while $P2M$ contains 2 fold rotation and a mirror symmetry (see Figure XXX). Two of the groups start with a $C$ rather than a $P$, ($CM$ and $CMM$) which indicates that the symmetries are specified relative to a cell that itself contains repetition.}

In mathematical group theory, when the elements of one group is completely contained in another, the inner group is called a subgroup of the outer group \citep{RN1425}. The full list of subgroup relationships is listed in Section 1.4.2 of the Supplementary Material. Subgroup relationships between wallpaper groups can be distinguished by their indices. The index of a subgroup relationship is the number of cosets, i.e. the number of times the subgroup is found in the supergroup \citep{RN1425}. As an example, let us consider groups \textit{P2} and \textit{P6}. If we ignore the translations in two directions that both groups share, group \textit{P6} consists of the set of rotations \{$0^{\circ}$, $60^{\circ}$, $120^{\circ}$, $180^{\circ}$, $240^{\circ}$, $300^{\circ}$\}, in which \textit{P2} \{$0^{\circ}$, $180^{\circ}$\} is contained. \textit{P2} is thus a subgroup of \textit{P6}, and \textit{P6} can be generated by combining \textit{P2} with rotations \{$0^{\circ}$, $120^{\circ}$, $240^{\circ}$\}. Because \textit{P2} is repeated three times in \textit{P6}, \textit{P2} is a subgroup of \textit{P6} with index 3 \citep{RN1425}. The 17 wallpaper groups thus obey a hierarchy of complexity where simpler groups are subgroups of more complex ones \citep{RN1711}.
